Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-08-31 doc/paper.tex
minor fix

       In order to improve the results of the Greedy heuristic, we propose a hybridization with the LS method. 
       The pseudocode is given in Algorithm~\ref{alg: hybrid-ls-greedy}.
        \begin{algorithm}[!t]
       	\caption{Local Search}\label{alg:hybrid-ls-greedy}
       	\begin{algorithmic}
       		   	\State \textbf{Input:} and Instance of the problem; $pct$:percentage
       		    \State \textbf{Output:} a complete solution $s$
       		    \State $s_{greedy} \gets \emptyset$
       		    \While{ $s_{greedy}$ is not complete}
       		        \State $s^P \gets$ call Greedy to expend $s_{greedy}$ for (up to) $\lfloor n \cdot p \rfloor$ guards 
       		        \State $s_{greedy} \gets$ LS($s^P$)
       		    \EndWhile
       \end{algorithmic}
       \end{algorithm}

>>>>

       In order to improve the results of the Greedy heuristic, we propose a hybridization with the LS method. 
       The pseudocode is given in Algorithm~\ref{alg: hybrid-ls-greedy}.
        \begin{algorithm}[!t]
       	\caption{Local Search + Greedy}\label{alg:hybrid-ls-greedy}
       	\begin{algorithmic}
       		   	\State \textbf{Input:} and Instance of the problem; $pct\in (0,1)$:percentage
       		    \State \textbf{Output:} a complete solution $s$
       		    \State $s_{greedy} \gets \emptyset$
       		    \While{ $s_{greedy}$ is not complete}
       		        \State $s^P \gets$ call Greedy to expend $s_{greedy}$ for (up to) $\lfloor n \cdot pct \rfloor$ guards 
       		        \State $s_{greedy} \gets$ LS($s^P$)
       		    \EndWhile
       \end{algorithmic}
       \end{algorithm}
